An Evolutionary Algorithm for the Multiobjective Risk-Equity Constrained Routing Problem

### 2011-11-29 DAW_hazmatHypE/trunk/paper/hazmatRouting_EvolOptim.tex
added first version of abstract, deleted planned section on comparison with exact approaches due to missing results

\begin{abstract}
tbw
\end{abstract}

\begin{keyword}
Evolutionary multiobjective optimization, Transportation of hazardous materials, Risk equity, Shortest Paths. 
\end{keyword}

@@

\subsection{Comparison With An Exact Algorithm for the Two Linear Objectives}
\TODO{add plots and describe what we compare (efficient cost/risk paths multiplied by the number of trucks); result: EA is better}

>>>>

\begin{abstract}
Nowadays, various hazardous materials, or \emph{hazmats}, are transported on our streets, via trains, planes or ships. In paricular when routing them over the street network, where typically several possible routes exist, one would like to minimize both the costs and the total risks. However, sometimes one aims at minimizing an additional type of risk, which in most optimization models is resulting in a non-linear objective: the equity risk, or the \emph{maximum} risk over all regions, streets, etc. In other words, one aims at distributing the overall risks as much as possible while the costs and the total risk should be still minimized simultaneously. In this paper, this three-objective optimization problem is tackled with a novel randomized algorithm, based on a state-of-the-art Evolutionary Multiobjective Optimization algorithm and taylored to the needs of finding Pareto-optimal truck routes in a given network by proposing a variable-length representation and problem-specific operators. Experimental results on realistic instances for the street network of Italy's Lazio region show that the proposed approach efficiently finds a variety of good solutions in reasonable time. The experiments also show the influence of the algorithm's different building blocks and the instances' parameters on the solution quality.
\end{abstract}

\begin{keyword}
Evolutionary Multiobjective Optimization, Transportation of hazardous materials, Risk equity, Shortest Paths. 
\end{keyword}

@@
